---
title: "Midpoint Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library("knitr")
source("scripts/summary_data.R")
source("scripts/summarytable.R")
source("scripts/piechart.R")
source("scripts/platform_checker.R")
source("scripts/scatter_plot.R")
```

## Introduction

Recommendation systems are a relatively new occurrence that have become a 
necessity when using modern day media platforms. One of the most famous 
examples of this is movie recommendations, present on a variety of video 
streaming services such as Netflix, Hulu, and HBO. As students interested in 
data science and the applications thereof, as well as being avid consumers of 
movies ourselves, we would like to see how we could develop our own movie 
recommendation program. Prior to writing all the scripts/functions, we have 
cleaned and merged the raw data sets. The most recent versions are named
`movies_ratings_platforms.csv` and `movies_ratings_platforms_top1000.csv`.


## Summary Information Script

```{r, echo=FALSE}
summary_info(mrp_top1000)
```

We created a summary information function to compute useful information
about our movie platform data sets. When run on our cleaned version;
`movies_ratings_platforms_top1000.csv` data set, we find that the data set has
`r n_col` total columns, the titles of each being: `r col_names`. The main
columns we will use for analysis are `weighted_average_vote` and `Meta_score`.
The average value for IMdb rating and meta score are `r mean_imdb` and 
`r mean_meta`, respectively. For `r mean_imdb`, this is from a range of 
`r highest_imdb` (high) to `r lowest_imdb` (low). The data set also consists of 
`r n_rows` movies, but as some movies are repeats, there are only actually 
`r n_movies` movies. Of the available movies, the most certificates 
are `r top_4_certificates` from most to least.

## Aggregate Table Script

```{r, echo=FALSE}
kable(summary_table(movie_data))
```

This table summarizes the information of each movie, such as the movie name,
the genre, weighted average vote, metascore, duration, and whether the movie
is on each platform(Netflix, Hulu, Prime Video, and Disney). 

## Chart Script (1) - Pie Chart

This pie chart shows the popularity of each genre based on the movies that are
rated above 7.0. The result shows that among those movies that are rated 7.0 or
higher, 43.3% are Drama, 24.9% are Comedy, 16.9% are Action, 13.4% are Romance,
and 1.5% are Horror. The genre Drama is the most popular and Horror is the least
popular among high-rated movies.

```{r, echo=FALSE}
pie_chart(movie_platform, movie_top)
```

The numbers around the pie chart represent the number of movies in each genre.

## Chart Script (2) - Bar Chart

This bar chart is used to express binary variables. In other words, to show
whether a movie is "on" or "not on" a certain platform. Bar chart is good for
this intention, because it allows users to quickly spot the difference in value.
Below is an example bar char that checks on the movie `A Christmas Prince`.

```{r, echo=FALSE}
platform_check("A Christmas Prince", movies_ratings_platforms)
```

The bar chart shows the platforms: Netflix, Disney., Hulu, Prime.Video and
illustrate whether a certain movie is on or not on those platform.

## Chart Script (3) - Scatter Plot

This plot chart attempts to express the most popular movies available on every
streaming platform. This expresses the types of streaming service data that
we have access to, and demonstrates the capability of sorting the overall
data frame for specific values as well as combining them afterwords.
Scatter plots were used for this display because of the many data points
specific numerical values, and multiple categories (platforms).

```{r, echo=FALSE, warning=FALSE}
popular_movies(mrp_top1000)
```

The scatter plot displays the top 5 movies from every streaming service.
The points contain the name and rating of the movie (when hovered), and are
color coded by streaming service. The y values are the movie ratings.
